---
title: "Causal Impact R Notebook"
output: html_notebook
---


```{r}
# The easiest way to get dplyr is to install the whole tidyverse:
#install.packages("tidyverse")

# Alternatively, install just dplyr:
#install.packages("dplyr")

#install.packages("CausalImpact")
```


## Load Packages 
```{r}
library(DBI) #for connect to Oracle databases
library(dplyr)
library(MASS)
library(broom) #for tidy()function
library(rpart)
library(tibble)
library(tidyr)
library(corrr)
library(knitr)
library(CausalImpact)

for(pkg in c("ggplot2", "dplyr")){
  library(pkg, character.only = TRUE)
}

```



# Load Data
```{r}
# 1. Query using DBI

df <- read.csv(file = 'CausalExercise.csv') # data file has to be placed in the same directory

#head(df)

# view summary statistics and data
summary(df)
str(df)
View(df)


# Count missing values on original data set 
apply(df, 2, function(x) sum(is.na(x)))

# view data types
sapply(df, class)

# check datatype 
class(df)

min(df$Date)
max(df$Date)

```


The detail attributes of the dataset :
- Date : the time
- IBCL : Variable interest today (the rate at which banks borrow or lend from each other)
- US10Year : 10 year yield of the US Government fund (covariates)
- VIX : (covariates)

The covariates are essentially a variable that sort of co-move in the same way with the IBCL does, but they’re not directly related to the treatment.


# Reformat data

```{r}
# https://rdrr.io/r/base/seq.Date.html#:~:text=seq.Date%20R%20Documentation%20Generate%20Regular%20Sequences%20of%20Dates,to%2C%20by%2C%20length.out%20%3D%20NULL%2C%20along.with%20%3D%20NULL%2C...%29

# Modify the date with “yyyy-mm-dd” format and then declare the time series variables
time.points <- seq.Date(as.Date("2020-02-27"), by = 1, length.out=44)

ibcl <- ts(df$IBCL)
u10yr <- ts(df$US10Year)
vix <- ts(df$VIX)

#Bind the data
class(time.points)
data <- zoo(cbind(ibcl, u10yr, vix), time.points)
head(data)
```
#Set pre and the post intervention periods.

The pre period is the period before a certain policy action was implemented.
The post period is the period after the policy action.

```{r}

pre.period <- as.Date(c("2020-02-27", "2020-03-23"))
post.period <- as.Date(c("2020-03-24", "2020-04-10"))

```



# Determine the causalimpact and calculate the impact between the pre-period to the post period
```{r}

impact <- CausalImpact(data, pre.period, post.period)
impact

plot(impact)

```




# Summarize results
```{r}
summary(impact)
summary(impact, "report")
```















